How to compute the fusion product of MV cycles in type A

### 2021-03-01 draft.tex
Updates from Overleaf

\subsection{Lattices}
\label{ss:lat}
We will use the lattice model, so it is useful to recall the following definition. Let $ R \subset K$ be two rings (usually, but not always, $K$ will be a field 
% \acom{When is $K$ not a field?}). Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and; e.g. K = C[t,t^{-1}] is not a field!!! 
Consider $ K^m $ as a $K$-module. By restriction $ K^m$ can be viewed as an $R$-module.  An $R$-lattice in $K^m$ 
% \acom{what is $M$? should be $K^m$?}; bc Joel was thinking about arbitrary free modules 
is an $R$-submodule $ L \subset K^m$ such that $ L $ is a free rank $ m $ $R$-module and $ L \otimes_R K = K^m $.  Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$. \jcom{Maybe need that both $K$ and $R$ are integral domains and have the same field of fractions?} \acom{Roger proved it.}
% is this true?

@@

    The fibre of $\Grbd \to \AA$ over $ s \in \AA $, for $ s \ne 0$, will be denoted $ \Gr_{0,s} $ and is given by \rcom{why do we have the $s\ne 0$ restriction here}
    % 
    $$ 
    \Gr_{0,s} = G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])\,. % := \pi^{-1}(s) 
    $$
    % \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
    % \jcom{Yes, that is one reason.  But also, there was a comment of yours before in the file, saying that you sometimes got confused that one point was fixed at 0, so this is a good notation to remind us (and the reader).  For the same reason, maybe we should write $ \Gr_{0, \AA}$ instead of $ \Gr_\AA$.}
    % \acom{lol}

@@

\acom{We will write only coset representatives for (orbits of) elements of the various Grassmannians; right cosets will be clear from context.}

% 
\begin{itemize}
    % \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 
    % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
    \item The lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$. 
    % In the lattice model, we have %  G(\cO); understood from context 
    $$ 
    L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
    $$ 
    \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ and its closure 
    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
    \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
    This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
    % 
    \item The family $ \overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} \rightarrow \AA$ defined by $ \overline{\Gr}^{\lambda_1, \lambda_2}_{0, \AA} = \overline{\Gr}^{\lambda_1} \ast_\AA \overline{\Gr}^{\lambda_2}$. 
    % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda_1}\times\overline\Gr^{\lambda_2}\times\AA^\times}$..}
    %\acom{should we also subsript this family with $0,\AA$?}

@@

    Suppose that $ s \ne 0$.  In the fibre $\overline{\Gr}_{0,s}^{\lambda_1, \lambda_2}$ we have the open locus $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ coming from transporting $ \Gr^{\lambda_1} \times \Gr^{\lambda_2} $ via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $.  This open locus is a $ G(\CC[t])$-orbit
    % .  The lattice description of $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ 
    whose lattice description is given in \Cref{le:Grl1l2} below.
    \acom{Why $G(\CC[t])$. Because we are on the left side!}

    \item The locus $\cW_\mu = G_1\xt[t^{-1}]L_\mu \subset \Grth $.  
    \acom{want $t^\mu\CC[t]$ as opposed to $L_\mu$ here? Use thick $L_0$, $L_\mu$. $t\in R$, $t^\mu L_0(R)$. Or just use $t^\mu$.}
    In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.  The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below.

    \acom{que est-ce?} \jcom{It's not very relevant for this paper.  Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN-filtration; it is a partial flag of subbundles of type determined by $ \mu$.  We require that $ \varphi$ takes this filtration to the standard partial flag at the fibre over $ \infty$.  Maybe ``preserves'' is not the best word above.}
    % A: Ok thanks!

    \item The semi-infinite orbit $ S^\mu = N(\cK)L_\mu \subset \Gr $.  
    \item The family of semi-infinite orbits $ S^{\mu_1, \mu_2}_{0,\AA} := S^{\mu_1} \ast_\AA S^{\mu_2}$.  If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
    $$
    S^{\mu_1, \mu_2}_{0,s} = N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} G(\CC[t])\subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
    $$
%    \acom{should be $G(\cO)$-coset or $G(\CC[t])$-coset?}
\jcom{Maybe we should introduce the $ L_{\mu_1, \mu_2} $ notation, but I'm not sure it is necessary.}
    On the other hand, if $ s = 0$, then the fibre $S^{\mu_1, \mu_2}_{0,0} $ equals $ S^{\mu_1 + \mu_2}$. \acom{changed $\mu$ to $\mu_1 + \mu_2$ since we wrote it out for $\overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} $}

@@

\begin{itemize}
    \item For $ s \in \CC$ and $\lambda\in P_{++}$ we have a Jordan form matrix $ J_{s,\lambda}$ with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$. \acom{$s\in\AA$?}
    % 
    \item The adjoint orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.  Its closure is $ \overline{\OO}^\lambda = \bigcup_{\lambda' \le \lambda} \OO^{\lambda'}$.
    % 
    \item For $ s \in \CC, s \ne 0$, the adjoint orbit $ \OO^{\lambda_1, \lambda_2}_{0,s}$ of matrices conjugate to $ J_{0,\lambda_1} \oplus J_{s,\lambda_2}$.  Its closure is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s} = \bigcup_{\lambda_1' \le \lambda_1, \lambda'_2 \le \lambda_2} \OO^{\lambda_1', \lambda'_2}_{0,s}$. \acom{$s\in\AA$?}
    % 
    \item A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda_1), (s,\lambda_2))$ if its matrix representatives lie in $ \OO^{\lambda_1, \lambda_2}_{0,s}$.
    % 
    \item The family of adjoint orbits $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \rightarrow \AA$ whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s}$ and whose fibre over 0 is $\overline{\OO}^\lambda$.  \jcom{We should justify why the 0 fibre is correct scheme-theoretically.} 
    \acom{does it follow because ``$s$ divides $\det g$'' is a closed condition 
    in $\AA_s\times \AA_{\det}$? 
    so the set of $A$ which are conjugate to
    $J_{0,\lambda_1} \oplus J_{s,\lambda_2}$
    by a matrix whose determinant is divisible by $s$ is also closed?}
    \jcom{I didn't follow your argument. One approach would be to write down the generators for the ideal of $\overline{\OO}^{\lambda_1, \lambda_2}_{0,s} $ and then set $ s =0$.  For example, take $ \lambda_1 = (1) = \lambda_2 $ (I know it is a small example!), then the ideal is generated by $ tr(A) = s$, $det(A) = 0$, so when we take $ s =0$, we get just $ tr(A) = 0, det(A) = 0$.  I am hoping that we can find a reference for this result somewhere.}
    \acom{I thought that the point would be to show that a dense subset of matrices which are conjugate to $J_{0,\lambda_1}\oplus J_{s,\lambda_2}$ limit to matrices which are conjugate to $J_\lambda$. In particular, that the conjugating matrix remains invertible in the $s\to0$ limit.}

@@

    \item The ``upper-triangular'' MVy slice $\TT^{\mu_1, \mu_2,+}_\AA \rightarrow \AA $, defined by
    $$
    \TT^{\mu_1, \mu_2,+}_\AA := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
    $$
    So a matrix in $\TT^{\mu_1, \mu_2,+}_\AA  $ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$.

    Note that the fibre $  \TT^{\mu_1, \mu_2,+}_{0,0}$ is the same as the intersection of $ T^\mu $ with the strictly upper triangular matrices.

    $\UU_{0,0}$ entries look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
            0 & 1 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0\\
            0 & 0 & 0 & A_{12}^1 & A_{12}^2\\
            0 & 0 & 0 & 0 & 1\\
            0 & 0 & 0 & 0 & 0
            \end{BMAT}\right]    \mapsto 
            \left[\begin{array}{rr}
                t^{3} & 0 \\
                -A_{12}^2 t - A_{12}^1 & t^{2}
            \end{array}\right]
    \]
    $\UU$ entries look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc;c}{ccc;cc;c} 
            0 & 1 & 0 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0 & 0\\
            0 & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
            0 & 0 & 0 & 0 & 1 & 0\\
            0 & 0 & 0 & 0 & s & A_{23}^1\\
            0 & 0 & 0 & 0 & 0 & s
            \end{BMAT}\right]    \in \UU_{0,s}^{(1,1,0),(2,1,1)}
    \]

@@

\begin{proof}
    % Copy Roger's proof.
    We have
\[
\begin{split}
    S_{\mu_1, \mu_2} & = N((t^{-1}))t^{\mu_1}(t-s)^{\mu_2} \\
     & \subset T_1[[t^{-1}]] N((t^{-1})) t^{\mu_1} (t-s)^{\mu_2} \\
     & = T_1[[t^{-1}]] N_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \qquad \text{\cite[Lemma 2.3]{kamnitzer2014yangians}}\\
     & = B_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \\
     & = B_1[[t^{-1}]] t^{\mu_1 + \mu_2} \\
     & \subset G_1[[t^{-1}]] t^{\mu_1 + \mu_2} \\
     & = W_{\mu_1 + \mu_2}
\end{split}
\]
where $B_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} = B_1[[t^{-1}]] t^{\mu_1 + \mu_2}$ since 
\[
\frac{t}{t-s} = 
1 + \frac{s}{t} + \frac{s^2}{t^2} + \cdots 
\in B_1[[t^{-1}]].
\]
\end{proof}

>>>>

\subsection{Lattices}
\label{ss:lat}
We will use the lattice model, so it is useful to recall the following definition. Let $ R \subset K$ be two rings (usually, but not always, $K$ will be a field 
% \acom{When is $K$ not a field?}). Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and; e.g. K = C[t,t^{-1}] is not a field!!! 
Consider $ K^m $ as a $K$-module. By restriction $ K^m$ can be viewed as an $R$-module.  An $R$-lattice in $K^m$ 
% \acom{what is $M$? should be $K^m$?}; bc Joel was thinking about arbitrary free modules 
is an $R$-submodule $ L \subset K^m$ such that $ L $ is a free rank $ m $ $R$-module and $ L \otimes_R K = K^m $.  Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$. \jcom{Maybe need that both $K$ and $R$ are integral domains and have the same field of fractions?} \acom{Roger proved it.}
\rcom{Here's my argument: If $L \subset K^m$ is a free rank $m$ $R$-module and $L \otimes K = K^m$, then it's clear that $L$ is generated by $m$ generators $v_1,\dots,v_m$ over $R$. Since $L\otimes K = K^m$, these also generate $K^m$ over $K$. Then we have a surjective map $K^m \twoheadrightarrow K^m$ given by sending a basis of $K^m$ to the generators $v_1,\dots,v_m$. Since any surjective endomorphism of finite $K$-modules is injective, the $v_1,\dots,v_m$ form a basis. I think the only thing that is needed is that the rings are commutative.}
% is this true?

@@

    The fibre of $\Grbd \to \AA$ over $ s \in \AA $, for $ s \ne 0$, will be denoted $ \Gr_{0,s} $ and is given by \rcom{Why do we have the $s\ne 0$ restriction here? We use $\Gr_{0,0}$ later.}
    % 
    $$ 
    \Gr_{0,s} = G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])\,. % := \pi^{-1}(s) 
    $$
    % \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
    % \jcom{Yes, that is one reason.  But also, there was a comment of yours before in the file, saying that you sometimes got confused that one point was fixed at 0, so this is a good notation to remind us (and the reader).  For the same reason, maybe we should write $ \Gr_{0, \AA}$ instead of $ \Gr_\AA$.}
    % \acom{lol}

@@

We will write only coset representatives for (orbits of) elements of the various Grassmannians; right cosets will be clear from context.

% 
\begin{itemize}
    % \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 
    % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
    \item The lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$. 
    % In the lattice model, we have %  G(\cO); understood from context 
    $$ 
    L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
    $$ 
    \item The orbit $\Gr^\lambda = G(\cO) t^\lambda$ and its closure % L_\lambda
    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
    % \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
    This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
    % 
    \item The family $ \overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} \rightarrow \AA$ defined by $ \overline{\Gr}^{\lambda_1, \lambda_2}_{0, \AA} = \overline{\Gr}^{\lambda_1} \ast_\AA \overline{\Gr}^{\lambda_2}$. 
    % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda_1}\times\overline\Gr^{\lambda_2}\times\AA^\times}$..}
    %\acom{should we also subsript this family with $0,\AA$?}

@@

    Suppose that $ s \ne 0$.  In the fibre $\overline{\Gr}_{0,s}^{\lambda_1, \lambda_2}$ we have the open locus $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ coming from transporting $ \Gr^{\lambda_1} \times \Gr^{\lambda_2} $ via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $.  This open locus is a $ G(\CC[t])$-orbit
    % .  The lattice description of $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ 
    whose lattice description is given in \Cref{le:Grl1l2} below.
    % \acom{Why $G(\CC[t])$. Because we are on the left side!}

    \item The locus $\cW_\mu = G_1\xt[t^{-1}] t^\mu \subset \Grth $. % L_\mu
    % \acom{want $t^\mu\CC[t]$ as opposed to $L_\mu$ here? Use thick $L_0$, $L_\mu$. $t\in R$, $t^\mu L_0(R)$. Or just use $t^\mu$.}
    In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.  The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below.

    \acom{que est-ce?} \jcom{It's not very relevant for this paper.  Here is an explanation: every vector bundle on $\PP$ (or maybe any curve) has a special filtration called the HN-filtration; it is a partial flag of subbundles of type determined by $ \mu$.  We require that $ \varphi$ takes this filtration to the standard partial flag at the fibre over $ \infty$.  Maybe ``preserves'' is not the best word above.}
    % A: Ok thanks!
    \acom{c.f.\ the lattice description for the ordinary $\Gr$. 
    $$G_1[t^{-1}] t^\mu = \{L\in \Gr : L = \Sp_{\cO}(v_1,\dots,v_m) \text{ such that }  v_j = t^{\mu_j} e_j + \sum p_{ij} e_i \text{ with  } \deg p_{ij} < \mu_j \}$$}

    \item The semi-infinite orbit $ S^\mu = N(\cK) t^\mu \subset \Gr $. % L_\mu  
    \item The family of semi-infinite orbits $ S^{\mu_1, \mu_2}_{0,\AA} := S^{\mu_1} \ast_\AA S^{\mu_2}$.  
    If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
    $$
    S^{\mu_1, \mu_2}_{0,s} = N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2} \subset G(\CC[t,t^{-1}, (t-s)^{-1}]) / G(\CC[t]) \,. % \G(\CC[t])
    $$
%    \acom{should be $G(\cO)$-coset or $G(\CC[t])$-coset?}
\jcom{Maybe we should introduce the $ L_{\mu_1, \mu_2} $ notation, but I'm not sure it is necessary.} \acom{Unless we need to describe the corresponding lattice?}
    On the other hand, if $ s = 0$, then the fibre $S^{\mu_1, \mu_2}_{0,0} $ equals $ S^{\mu_1 + \mu_2}$. \acom{changed $\mu$ to $\mu_1 + \mu_2$ since we wrote it out for $\overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} $}

@@

\begin{itemize}
    \item For $ s \in \CC$ and $\lambda\in P_{++}$ we have a Jordan form matrix $ J_{s,\lambda}$ with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$. \acom{$s\in\AA$?}
    % 
    \item The adjoint orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.  Its closure is $ \overline{\OO}^\lambda = \bigcup_{\lambda' \le \lambda} \OO^{\lambda'}$.
    % 
    \item For $ s \in \CC, s \ne 0$, the adjoint orbit $ \OO^{\lambda_1, \lambda_2}_{0,s}$ of matrices conjugate to $ J_{0,\lambda_1} \oplus J_{s,\lambda_2}$.  Its closure is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s} = \bigcup_{\lambda_1' \le \lambda_1, \lambda'_2 \le \lambda_2} \OO^{\lambda_1', \lambda'_2}_{0,s}$. \acom{$s\in\AA$?}
    \end{itemize}
    % 
    A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space $V$ is said to have Jordan type $((0,\lambda_1), (s,\lambda_2))$ if its matrix representatives lie in $ \OO^{\lambda_1, \lambda_2}_{0,s}$.
    % 
    \begin{itemize}
    \item The family of adjoint orbits $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,\AA} \rightarrow \AA$ whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s}$ and whose fibre over 0 is $\overline{\OO}^\lambda$.  \jcom{We should justify why the 0 fibre is correct scheme-theoretically.} 
    \acom{does it follow because ``$s$ divides $\det g$'' is a closed condition 
    in $\AA_s\times \AA_{\det}$? 
    so the set of $A$ which are conjugate to
    $J_{0,\lambda_1} \oplus J_{s,\lambda_2}$
    by a matrix whose determinant is divisible by $s$ is also closed?}
    \jcom{I didn't follow your argument. One approach would be to write down the generators for the ideal of $\overline{\OO}^{\lambda_1, \lambda_2}_{0,s} $ and then set $ s =0$.  For example, take $ \lambda_1 = (1) = \lambda_2 $ (I know it is a small example!), then the ideal is generated by $ tr(A) = s$, $det(A) = 0$, so when we take $ s =0$, we get just $ tr(A) = 0, det(A) = 0$.  I am hoping that we can find a reference for this result somewhere.}
    \acom{I thought that the point would be to show that a dense subset of matrices which are conjugate to $J_{0,\lambda_1}\oplus J_{s,\lambda_2}$ limit to matrices which are conjugate to $J_\lambda$. In particular, that the conjugating matrix remains invertible in the $s\to0$ limit.}

    \acom{\ul{see what} \cite{weyman1989equations} does.}

@@

    \item The ``upper-triangular'' MVy slice $\UU^{\mu_1, \mu_2}_\AA \rightarrow \AA $, defined by \acom{maybe can do without 0 subscript on $\UU$, adding in for analogy}
    $$
    \UU^{\mu_1, \mu_2}_{0,\AA} := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
    $$
    So a matrix in $\UU^{\mu_1, \mu_2}_{0,\AA}  $ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$. The fibre over $s$ is denoted by $\UU^{\mu_1, \mu_2}_{0,s}$.

    Note that the fibre $  \UU^{\mu_1, \mu_2}_{0,0}$ is the same as the intersection of 
    % $ T^\mu $ % TODO: we mean TT_\mu right?
    $\TT_\mu$ with the strictly upper triangular matrices.

    $\UU^{\mu_1,\mu_2}_{0,0}$ entries look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc}{ccc;cc} 
            0 & 1 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0\\
            0 & 0 & 0 & A_{12}^1 & A_{12}^2\\
            0 & 0 & 0 & 0 & 1\\
            0 & 0 & 0 & 0 & 0
            \end{BMAT}\right]    \in \UU^{(3,2)}_{0,0}
            % \mapsto 
            % \left[\begin{array}{rr}
            %     t^{3} & 0 \\
            %     -A_{12}^2 t - A_{12}^1 & t^{2}
            % \end{array}\right]
    \]
    $\UU^{\mu_1,\mu_2}_{0,s}$ entries look like 
    \[
        \left[\begin{BMAT}(e){ccc;cc;c}{ccc;cc;c} 
            0 & 1 & 0 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0 & 0\\
            0 & -s^2 & 2s & A_{12}^1 & A_{12}^2 & A_{13}^1 \\
            0 & 0 & 0 & 0 & 1 & 0\\
            0 & 0 & 0 & 0 & s & A_{23}^1\\
            0 & 0 & 0 & 0 & 0 & s
            \end{BMAT}\right]    \in \UU_{0,s}^{(1,1,0),(2,1,1)}
    \]

@@

\begin{proof}
    % Copy Roger's proof.
    We have
\[
\begin{split}
    S_{\mu_1, \mu_2} & = N\xT[t^{-1}]t^{\mu_1}(t-s)^{\mu_2} \\
     & \subset T_1\xt[t^{-1}] N\xT[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
     & = T_1\xt[t^{-1}] N_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \qquad \text{\cite[Lemma 2.3]{kamnitzer2014yangians}}\\
     & = B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} \\
     & = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
     & \subset G_1\xt[t^{-1}] t^{\mu_1 + \mu_2} \\
     & = W_{\mu_1 + \mu_2}
\end{split}
\]
where $B_1\xt[t^{-1}] t^{\mu_1} (t-s)^{\mu_2} = B_1\xt[t^{-1}] t^{\mu_1 + \mu_2}$ since 
\[
\frac{t}{t-s} = 
1 + \frac{s}{t} + \frac{s^2}{t^2} + \cdots 
\in B_1[[t^{-1}]].
\]
\end{proof}
